---
title: "06_1_make_simulation_data"
author: "Suguru Otani"
date: "2024-01-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load {.tabset}

```{r, echo=FALSE,results = "asis"}
rm(list = ls())
library(magrittr)
library(ggplot2)
library(modelsummary) # for N in datasummary
list_num_time <-
  c(
    # 10,
    # 20,
    # 30,
    # 40,
    50,
    100,
    200
  )
specification_list <-
  c(
    "cobb_douglas",
    "perfect_substitute",
    "fixed_proportion"
  )
## set stationarity parameter ----
arima_list <-
  list(
    "AR1_I0" = c(1,0,0),
    #"AR1_I1" = c(1,1,0),
    "AR0_I1" = c(0,1,0)
    )
## set independence parameter ----
dependency_V_of_A_list <-
  c(
    0,
    0.1,
    0.2
  )

# load, estimate, and save data ----
for(nn in 1:length(list_num_time)){
  for(mm in 1:length(specification_list)){
    for(rr in 1:length(arima_list)){
      for(qq in 1:length(dependency_V_of_A_list)){
        dependency_V_of_A <-
          dependency_V_of_A_list[qq]
        target_arima <-
          arima_list[[rr]]
        target_arima_name <-
          names(arima_list)[rr]
        CRS_gamma_parameter <-
        0.3
        temp_nn <-
          list_num_time[nn]
        matching_function_specification <-
          specification_list[mm]
        filename <-
            paste(
              #"output/monte_carlo_data_",
              "num_time_",
              temp_nn,
              "_",
              matching_function_specification,
              "_",
              CRS_gamma_parameter,
              "_",
              target_arima_name,
              "_",
              "va_dependency_",
              dependency_V_of_A,
              sep = ""
            )
        cat(filename,"\n")
        # load 
        target_data <-
          readRDS(
            file = 
              here::here(
                paste(
                  "output/",
                  "monte_carlo_data_",
                  filename,
                  ".rds",
                  sep = ""
                )
              )
          )
        assign(filename,
               target_data)
      }
      
    }
    
  }
}

plot_target_data <-
  function(
    target_data,
    target_variable
    ){
    target_plot <- 
      ggplot(
        target_data %>% 
          dplyr::filter(simulation_id <= 10),
        aes(
          x = time,
          y = .data[[target_variable]],
          color = simulation_id, 
          group = simulation_id
          )
        ) +
      geom_line(
        alpha = 0.9, 
        size = 0.5
        ) + 
      # geom_point(
      #   aes(
      #     shape = industry_group_name,
      #     color = industry_group_name
      #     )
      #   ) +
      theme_classic() + 
      #scale_color_viridis_d() +
      theme(legend.position = 'top',
            legend.text = element_text(size=8)) +
      theme(axis.text.x = element_text(angle=60, vjust=1, hjust=1, size=6.0)) +
      xlab("")
    return(target_plot)
    
  }
```

## ARIMA (1,0,0) va dependency 0 {.tabset}

### cobb_douglas {.tabset}

#### num_time_50_cobb_douglas_0.3_AR1_I0_va_dependency_0  {.tabset}

the match elasticity with respect to unemployment is in the range 0.5–0.7.

##### unemployed

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_cobb_douglas_0.3_AR1_I0_va_dependency_0,
  "unemployed"
  )
```

##### position_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_cobb_douglas_0.3_AR1_I0_va_dependency_0,
  "vacancy"
  )
```


##### hire_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_cobb_douglas_0.3_AR1_I0_va_dependency_0,
  "hire"
  )

```

##### normalized_efficiency

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_cobb_douglas_0.3_AR1_I0_va_dependency_0,
  "normalized_efficiency"
  )
```

#### num_time_100_cobb_douglas_0.3_AR1_I0_va_dependency_0  {.tabset}

##### unemployed

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_cobb_douglas_0.3_AR1_I0_va_dependency_0,
  "unemployed"
  )
```

##### position_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_cobb_douglas_0.3_AR1_I0_va_dependency_0,
  "vacancy"
  )
```


##### hire_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_cobb_douglas_0.3_AR1_I0_va_dependency_0,
  "hire"
  )

```

##### normalized_efficiency

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_cobb_douglas_0.3_AR1_I0_va_dependency_0,
  "normalized_efficiency"
  )
```

### perfect_substitute {.tabset}

#### num_time_50_perfect_substitute_0.3_AR1_I0_va_dependency_0  {.tabset}

the match elasticity with respect to unemployment is in the range 0.5–0.7.

##### unemployed

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_perfect_substitute_0.3_AR1_I0_va_dependency_0,
  "unemployed"
  )
```

##### position_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_perfect_substitute_0.3_AR1_I0_va_dependency_0,
  "vacancy"
  )
```


##### hire_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_perfect_substitute_0.3_AR1_I0_va_dependency_0,
  "hire"
  )

```

##### normalized_efficiency

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_perfect_substitute_0.3_AR1_I0_va_dependency_0,
  "normalized_efficiency"
  )
```

#### num_time_100_perfect_substitute_0.3_AR1_I0_va_dependency_0  {.tabset}

##### unemployed

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_perfect_substitute_0.3_AR1_I0_va_dependency_0,
  "unemployed"
  )
```

##### position_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_perfect_substitute_0.3_AR1_I0_va_dependency_0,
  "vacancy"
  )
```


##### hire_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_perfect_substitute_0.3_AR1_I0_va_dependency_0,
  "hire"
  )

```

##### normalized_efficiency

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_perfect_substitute_0.3_AR1_I0_va_dependency_0,
  "normalized_efficiency"
  )
```

## ARIMA (0,1,0) i.e. nonstationary {.tabset}

### cobb_douglas {.tabset}

#### num_time_50_cobb_douglas_0.3_AR0_I1_va_dependency_0  {.tabset}

the match elasticity with respect to unemployment is in the range 0.5–0.7.

##### unemployed

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_cobb_douglas_0.3_AR0_I1_va_dependency_0,
  "unemployed"
  )
```

##### position_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_cobb_douglas_0.3_AR0_I1_va_dependency_0,
  "vacancy"
  )
```


##### hire_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_cobb_douglas_0.3_AR0_I1_va_dependency_0,
  "hire"
  )

```

##### normalized_efficiency

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_cobb_douglas_0.3_AR0_I1_va_dependency_0,
  "normalized_efficiency"
  )
```

#### num_time_100_cobb_douglas_0.3_AR0_I1_va_dependency_0  {.tabset}

##### unemployed

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_cobb_douglas_0.3_AR0_I1_va_dependency_0,
  "unemployed"
  )
```

##### position_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_cobb_douglas_0.3_AR0_I1_va_dependency_0,
  "vacancy"
  )
```


##### hire_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_cobb_douglas_0.3_AR0_I1_va_dependency_0,
  "hire"
  )

```

##### normalized_efficiency

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_cobb_douglas_0.3_AR0_I1_va_dependency_0,
  "normalized_efficiency"
  )
```

### perfect_substitute {.tabset}

#### num_time_50_perfect_substitute_0.3_AR0_I1_va_dependency_0  {.tabset}

the match elasticity with respect to unemployment is in the range 0.5–0.7.

##### unemployed

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_perfect_substitute_0.3_AR0_I1_va_dependency_0,
  "unemployed"
  )
```

##### position_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_perfect_substitute_0.3_AR0_I1_va_dependency_0,
  "vacancy"
  )
```


##### hire_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_perfect_substitute_0.3_AR0_I1_va_dependency_0,
  "hire"
  )

```

##### normalized_efficiency

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_50_perfect_substitute_0.3_AR0_I1_va_dependency_0,
  "normalized_efficiency"
  )
```

#### num_time_100_perfect_substitute_0.3_AR0_I1_va_dependency_0  {.tabset}

##### unemployed

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_perfect_substitute_0.3_AR0_I1_va_dependency_0,
  "unemployed"
  )
```

##### position_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_perfect_substitute_0.3_AR0_I1_va_dependency_0,
  "vacancy"
  )
```


##### hire_count

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_perfect_substitute_0.3_AR0_I1_va_dependency_0,
  "hire"
  )

```

##### normalized_efficiency

```{r,echo=FALSE,results = "asis"}
plot_target_data(
  num_time_100_perfect_substitute_0.3_AR0_I1_va_dependency_0,
  "normalized_efficiency"
  )
```
