---
title: "07_construct_figuretable_simulation"
author: "Suguru Otani"
date: "2024-01-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load {.tabset}

```{r, echo=FALSE,results = "asis"}
rm(list = ls())
library(magrittr)
library(ggplot2)
# set constant ----
list_num_time <-
  c(
    #10,
    #20,
    #30,
    #40,
    50,
    100,
    200
  )
specification_list <-
  c(
    "cobb_douglas",
    "perfect_substitute"#,
    #"fixed_proportion"
  )
CRS_gamma_parameter <-
  0.3#0.001
arima_list <-
  list(
    "AR1_I0" = c(1,0,0),
    #"AR1_I1" = c(1,1,0),
    "AR0_I1" = c(0,1,0)
  )
for(nn in 1:length(list_num_time)){
  for(mm in 1:length(specification_list)){
    for(rr in 1:length(arima_list)){
      target_arima <-
        arima_list[[rr]]
      target_arima_name <-
        names(arima_list)[rr]
      CRS_gamma_parameter <-
      0.3
    temp_nn <-
      list_num_time[nn]
    matching_function_specification <-
      specification_list[mm]
    temp_nn <-
      list_num_time[nn]
    filename <-
      paste(
        #"output/monte_carlo_data_",
        "num_time_",
        temp_nn,
        "_",
        matching_function_specification,
        "_",
        CRS_gamma_parameter,
        "_",
        target_arima_name,
        sep = ""
      )
    cat(filename,"\n")
    temp_data <-
      readRDS(
        file =
          here::here(
            paste(
              "output/",
              "implied_efficiency_",
              filename,
              ".rds",
              sep = ""
            )
            )
        )
    assign(
      filename,
      temp_data)
      }
    
  }
}
generate_bias_rmse <-
  function(target_data){
    res <-
      target_data %>% 
      dplyr::mutate(
        error = normalized_efficiency - efficiency_implied
        ) %>% 
      dplyr::group_by(
        simulation_id
      ) %>% 
      dplyr::summarise(
        bias =
          mean(error),
        rmse =
          sqrt(mean((error)^2, na.rm = TRUE))
      ) %>% 
      dplyr::ungroup()
    return(res)
  }

plot_target_data <-
  function(
    target_data,
    target_variable
    ){
    target_plot <- 
      ggplot(
        target_data %>% 
          dplyr::filter(simulation_id <= 10) %>% 
          dplyr::mutate(
            error_efficiency = normalized_efficiency - efficiency_implied
            ),
        aes(
          x = time,
          y = .data[[target_variable]],
          color = simulation_id, 
          group = simulation_id
          )
        ) +
      geom_line(
        alpha = 0.9, 
        size = 0.5
        ) + 
      # geom_point(
      #   aes(
      #     shape = industry_group_name,
      #     color = industry_group_name
      #     )
      #   ) +
      theme_classic() + 
      #scale_color_viridis_d() +
      theme(legend.position = 'top',
            legend.text = element_text(size=8)) +
      theme(axis.text.x = element_text(angle=60, vjust=1, hjust=1, size=6.0)) +
      xlab("")
    return(target_plot)
    
  }

options(modelsummary_format_numeric_latex = "plain") # for modelsummary output
```



## Appendix. Illustrative plot and num_time_100_cobb_douglas_0.3_AR1_I0 {.tabset}

the match elasticity with respect to unemployment is in the range 0.5–0.7.

### num_time_50_cobb_douglas_0.3_AR1_I0

```{r,echo=FALSE,results = "asis"}
# target_res <-
#   generate_bias_rmse(num_time_50_cobb_douglas_0.3_AR1_I0)
# modelsummary::datasummary_skim(
#   fmt = 3,
#   target_res
#   )
# plot_target <-
#   plot_target_data(
#     target_data = num_time_50_cobb_douglas_0.3_AR1_I0,
#     target_variable = "error_efficiency"
#     )
# plot_target

temp <-
  num_time_50_cobb_douglas_0.3_AR1_I0 %>% 
  dplyr::filter(
    simulation_id == 1
  ) %>% 
  dplyr::select(
    time, 
    normalized_efficiency,
    efficiency_implied
  )
x <- 
    ggplot(
    temp,
    aes(
      x = time,
      y = normalized_efficiency,
    color = "Efficiency (True)"
      )
    ) +
  geom_line(
    alpha = 0.9, 
    size = 0.5
    ) +
  geom_line(
    aes(
      x = time,
      y = efficiency_implied,
      color = "Efficiency Implied"  # This is the label name
    )
  ) +
  scale_color_manual(
    name = "",  # Title for the legend
    values = c("Efficiency Implied" = "red",
               "Efficiency (True)" = "black")  # Assign the color
  ) +
  labs(
    x = "Time",  # X-axis label
    y = "Efficiency Implied"  # Y-axis label
  ) +
  labs(colour = "") +
   theme(legend.position = 'top',
        legend.text = element_text(size=8))
x

figure_name <-
  "../figuretable/illustrative_plot_implied_efficiency_num_time_50_cobb_douglas_0.3_AR1_I0.png"
ggsave(filename = figure_name,
       plot = x,
       device = "png",
       width = 4,
       height = 3)
```

### num_time_100_cobb_douglas_0.3_AR1_I0

```{r,echo=FALSE,results = "asis"}
temp <-
  num_time_100_cobb_douglas_0.3_AR1_I0 %>% 
  dplyr::filter(
    simulation_id == 1
  ) %>% 
  dplyr::select(
    time, 
    normalized_efficiency,
    efficiency_implied
  )
x <- 
  ggplot(
    temp,
    aes(
      x = time,
      y = normalized_efficiency,
    color = "Efficiency (True)"
      )
    ) +
  geom_line(
    alpha = 0.9, 
    size = 0.5
    ) +
  geom_line(
    aes(
      x = time,
      y = efficiency_implied,
      color = "Efficiency Implied"  # This is the label name
    )
  ) +
  scale_color_manual(
    name = "",  # Title for the legend
    values = c("Efficiency Implied" = "red",
               "Efficiency (True)" = "black")  # Assign the color
  ) +
  labs(
    x = "Time",  # X-axis label
    y = "Efficiency Implied"  # Y-axis label
  ) +
  labs(colour = "") +
   theme(legend.position = 'top',
        legend.text = element_text(size=8))
x

figure_name <-
  "../figuretable/illustrative_plot_implied_efficiency_num_time_100_cobb_douglas_0.3_AR1_I0.png"
ggsave(filename = figure_name,
       plot = x,
       device = "png",
       width = 4,
       height = 3)
x
```





## Appendix. Illustrative plot and num_time_50_cobb_douglas_0.3_AR0_I1 {.tabset}

the match elasticity with respect to unemployment is in the range 0.5–0.7.

### num_time_50_cobb_douglas_0.3_AR0_I1

```{r,echo=FALSE,results = "asis"}
temp <-
  num_time_200_cobb_douglas_0.3_AR0_I1 %>% 
  dplyr::filter(
    simulation_id == 1
  ) %>% 
  dplyr::select(
    time, 
    normalized_efficiency,
    efficiency_implied
  )
x <- 
      ggplot(
        temp,
        aes(
          x = time,
          y = normalized_efficiency
          )
        ) +
      geom_line(
        alpha = 0.9, 
        size = 0.5
        ) +
  geom_line(
    aes(
          x = time,
          y = efficiency_implied,
          color = "red"
          )
        ) +
  xlab("") +
  ylab("mismatch") +
  labs(colour = "")
x
```

### num_time_100_cobb_douglas_0.3

```{r,echo=FALSE,results = "asis"}
target_res <-
  generate_bias_rmse(num_time_100_cobb_douglas_0.3_AR0_I1)
modelsummary::datasummary_skim(
  fmt = 3,
  target_res
  )
plot_target <-
  plot_target_data(
    target_data = num_time_100_cobb_douglas_0.3_AR0_I1,
    target_variable = "error_efficiency"
    )
plot_target
```


